---
title: "homework"
author: "Omid Karimi, Evan Aguzzi, Luca Bracone, Blerton Rashiti"
date: "2021-04-08 <-- doit changer"
output: pdf_document
---

```{r, echo = FALSE}
library("MASS")
air <- read.delim("airline_costs.dat", header = FALSE, sep="")
colnames(air) <- c("Airline", "LoF", "SoP", "DFT", "population", "TOC", "RTpAM", "TMlf",
                    "capacity", "totassets", "investments", "adjassets")
```

# Exploratory phase

For each airline we have the following variables:

* Airline, the name of the airline.
* Total operating costs (`TOC`), normalized per revenue ton-mile (in cents).
* Length of Flight (`LoF`), in miles.
* Speed of Plane (`SoP`), in miles per hour.
* Daily flight time per plane (`DFT`), in hours.
* Population served(`population`).
* Revenue tons per aircraft mile(`RTpAM`), a measure of how much revenue a company earns by transporting one ton of cargo for one mile.
* Ton-Mile load factor (`TMlf`), the proportion of used space ..?
* Available capacity (`capacity`), measured in ton-miles



```{r, echo = F}
fit <- lm(TOC ~ capacity + LoF + TMlf + DFT + population + SoP + totassets, data = air)
fit2 <- lm(TOC ~ DFT, data = air)
a <- stepAIC(fit,fit2)
summary(a)
plot(a)
```
